---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cbp.analysis

<!-- badges: start -->
<!-- badges: end -->

The goal of cbp.analysis is to analyzes U.S. Customs and Border Protection (CBP) data.Through the analysis of cbp_resp data, we found significant differences in the distribution of different demographic characteristics (such as family unit members (FMUA), unaccompanied children (UC)) in border encounters.

## Installation

You can install the development version of cbp.analysis like so:

``` r
remotes::install_github("ETC5523-2024/supplementary-assignment-Qiuyuan0055")
```

## Example

This is a basic example which shows how to solve a common problem:

Example 1: Trends in Encounters for Unaccompanied Children
```{r}
# Filter and summarize data by fiscal year for "Unaccompanied Children"
uc_trends <- cbp_resp %>%
  filter(demographic == "Unaccompanied Children") %>%
  group_by(fiscal_year) %>%
  summarise(total_encounters = sum(encounter_count, na.rm = TRUE)) %>%
  ungroup()

# Plot trends for Unaccompanied Children
ggplot(uc_trends, aes(x = fiscal_year, y = total_encounters)) +
  geom_line(color = "blue", size = 1) +
  geom_point(size = 2) +
  theme_minimal() +
  labs(
    title = "Trends in Encounters for Unaccompanied Children",
    x = "Fiscal Year",
    y = "Total Encounters"
  ) +
  scale_x_continuous(breaks = seq(min(uc_trends$fiscal_year), max(uc_trends$fiscal_year), by = 1))

```
 Example 2: Top States by Total Encounters
```{r}
# Summarize data by state
state_summary <- cbp_state %>%
  group_by(state) %>%
  summarise(total_encounters = sum(encounter_count, na.rm = TRUE)) %>%
  arrange(desc(total_encounters))

# Plot top 10 states
top_states <- state_summary %>%
  slice_head(n = 10)

ggplot(top_states, aes(x = reorder(state, total_encounters), y = total_encounters)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Top 10 States by Total CBP Encounters",
    x = "State",
    y = "Total Encounters"
  ) +
  scale_y_continuous(labels = scales::comma)
```

# Result
```{r}
# Example 1: Trends in Encounters for Unaccompanied Children
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(scales)

# Ensure fiscal_year is numeric and remove missing values
cbp_resp <- cbp_resp %>%
  mutate(fiscal_year = as.numeric(fiscal_year)) %>%
  filter(!is.na(fiscal_year))

# Summarize encounters for "Unaccompanied Children" by fiscal year
uc_data <- cbp_resp %>%
  filter(demographic == "Unaccompanied Children") %>%
  group_by(fiscal_year) %>%
  summarise(total_encounters = sum(encounter_count, na.rm = TRUE)) %>%
  ungroup()

# Check if uc_data contains valid data
if (nrow(uc_data) > 0 && all(is.finite(uc_data$fiscal_year))) {
  # Plot the trend
  ggplot(uc_data, aes(x = fiscal_year, y = total_encounters)) +
    geom_line(color = "blue", size = 1) +
    geom_point(size = 2) +
    theme_minimal() +
    labs(
      title = "Trends in Encounters for Unaccompanied Children",
      x = "Fiscal Year",
      y = "Total Encounters"
    ) +
    scale_x_continuous(breaks = seq(min(uc_data$fiscal_year, na.rm = TRUE), 
                                    max(uc_data$fiscal_year, na.rm = TRUE), by = 1)) +
    scale_y_continuous(labels = comma)
} else {
  message("No valid data available for 'Unaccompanied Children'.")
}

# Example 2: Top 10 States by Total Encounters
# Ensure state column is valid and remove missing values
cbp_state <- cbp_state %>%
  filter(!is.na(state))

# Summarize total encounters by state
state_data <- cbp_state %>%
  group_by(state) %>%
  summarise(total_encounters = sum(encounter_count, na.rm = TRUE)) %>%
  arrange(desc(total_encounters))

# Select top 10 states
top_10_states <- state_data %>%
  slice_head(n = 10)

# Check if top_10_states contains valid data
if (nrow(top_10_states) > 0) {
  # Plot the top states
  ggplot(top_10_states, aes(x = reorder(state, total_encounters), y = total_encounters)) +
    geom_bar(stat = "identity", fill = "steelblue") +
    coord_flip() +
    theme_minimal() +
    labs(
      title = "Top 10 States by Total CBP Encounters",
      x = "State",
      y = "Total Encounters"
    ) +
    scale_y_continuous(labels = comma)
} else {
  message("No valid data available for state-level analysis.")
}
```
	1.	This example addresses a typical analytical challenge: examining annual trends within specific demographic groups.
	2.	The dataset was processed by filtering for the target demographic and aggregating the data by fiscal year using filter and group_by. This approach effectively highlights the yearly variations in the selected population.
	3.	The resulting visualization illustrates the total number of encounters per fiscal year, enabling users to identify patterns over time and explore potential factors driving these trends.
For more details about the package, please visit[here](https://etc5523-2024.github.io/supplementary-assignment-Qiuyuan0055/) 
